### 2017-01-11 robust-software.tex
Reworked the Reuse section with the package manager rule in mind; added a guideline to depend on stable software. Issue #31

In the spirit of code reuse and interoperability, developers often want
to reuse software written by others. 
With a few lines, a call
is made out to the other program and the results are incorporated into the
primary script. Using popular projects reduces the amount of code that
needs to be maintained and leverages the work done by the other software.

Unfortunately, reusing software introduces dependencies, which can
bring their own special pain.  The interface between two software
packages can also be a source of considerable frustration: all too
often, support requests descend into debugging errors produced by the
other project. 
In addition, every package someone has to install
before being able to use yours is a
possible (some would say ``likely'') source of frustration for some
potential user. The way the second program is invoked can throw up errors.
The program may not be in the user's path, or it may be an
older or newer version and produce results different than expected.
Windows users will be frustrated if you invoke \texttt{bash} or \texttt{sh} explicitly or
use shell-specific conventions like `*' expansion.
Even Linux-standard functions available vary slightly between
installs. For example, GNU \texttt{sort} is available on almost every
*nix distribution, but sorts differently depending on locale.

Despite these problems, software developers in research should
re-use existing software provided three guidelines are adhered to.
First, 
\textbf{make sure that you really need the auxiliary program}. If you are
executing GNU sort instead of figuring out how to sort lists in Python,
it may not be worth the pain of integration.

Second, \textbf{ensure the appropriate software and version is available}.
Early in execution, check whether the dependency is executable and whether the
version is compatible.
Either allow the user to
configure the exact path to the package, distribute the program with the
dependent software, or download it during installation using a
dependency management system (see Rule 5).

Finally, to ensure support on as many different operating systems as
possible, \textbf{use native functions for starting other processes}, such as
Java's \texttt{Runtime.exec} call, Python's \texttt{subprocess} module, and Perl's \texttt{system}
command, and be sure to capture and report the output of the subprocess's standard error
to facilitate debugging.

@@

Programmers routinely use build tools like Make, Rake, Maven, Ant or MS Build
to compile code, deploy applications, and automate other tasks.
These tools can also be used to manage runtime environments,
i.e.,
to check that the right versions of required packages are installed
and install or upgrade them if they are not.

>>>>

In the spirit of code reuse and interoperability, developers often want
to reuse software written by others. 
With a few lines, a call
is made out to another library or program and the results are incorporated into the
primary script. Using popular projects reduces the amount of code that
needs to be maintained and leverages the work done by the other software.

Unfortunately, reusing software (whether software libraries or separate executables)
introduces dependencies, which can
bring their own special pain. The interface between two software
packages can be a source of considerable frustration: all too
often, support requests descend into debugging errors produced by the
other project due to incompatible libraries, versions, or operating
systems~\cite{brown2013}. Even introducing libraries in the same programming
language can rely on software installed in the environment.

Despite these problems, software developers in research should
re-use existing software provided a few guidelines are adhered to.

First, 
\textbf{make sure that you really need the auxiliary program}. If you are
executing GNU sort instead of figuring out how to sort lists in Python,
it may not be worth the pain of integration. Reuse software that offers some
measurable improvement to your build environment.

Second, if launching an executable, \textbf{ensure the appropriate software and version is available}.
Either allow the user to
configure the exact path to the package, distribute the program with the
dependent software, or download it during installation using your
package manager.

Third, \textbf{ensure that reused software is robust}. Relying on erratic third
party libraries or software is a recipe for tears. Prefer software that follows
good software development practices, is open for support questions, and is
available from a stable repository using your package manager.

Exercise caution especially when transitioning across languages or using
separate executables, as they tend to be especially sensitive to operating
systems, environments, and locales.

@@

To compile code, deploy applications, and automate other tasks, 
programmers routinely use build tools like Make, Rake, Maven, Ant or MS Build.
These tools can also be used to manage runtime environments,
i.e.,
to check that the right versions of required packages are installed
and install or upgrade them if they are not.
As mentioned in the previous rule,
a package manager can mitigate some of the difficulties in software reuse.
